
---
pagetitle: "Publications"
toc: false
bibliography: publications.bib
csl: apa.csl
nocite: |
  @*
execute:
  echo: false
  warning: false
  message: false
---

```{=html}
<nav aria-label="breadcrumb">
  <ol class="breadcrumb">
    <li class="breadcrumb-item"><a href="index.html">Home</a></li>
    <li class="breadcrumb-item active" aria-current="page">Publications</li>
  </ol>
</nav>
```

**IEEE Copyright Notice**: Personal use of this material is permitted. Permission from IEEE must be obtained for all other uses, in any current or future media, including reprinting/republishing this material for advertising or promotional purposes, creating new collective works, for resale or redistribution to servers or lists, or reuse of any copyrighted component of this work in other works.

The most up-to-date publication can be found on my [Google Scholar](https://scholar.google.com/citations?hl=en&user=wgsX_zIAAAAJ){.text-primary .text-decoration-none .fw-bolder}  profile.

The source code for our work is publicly available at [ICC Github](https://github.com/icclabo?tab=repositories){.text-primary .text-decoration-none .fw-bolder}  profile.

## Selected Publications


### Wireless/WiFi Sensing
   - T. D. Gian, T. T. Dung, F. Restuccia, Q.-V. Pham, and V.-D. Nguyen, "TinySense: Effective CSI Compression for Scalable and Accurate Wi-Fi Sensing," in *Proc. IEEE International Conference on Pervasive Computing and Communications (PerCom)*, Pisa, Italy, Mar. 2026, pp.1-10. [ArXiv](https://arxiv.org/abs/2601.15838){.text-primary .text-decoration-none .fw-bolder}
   - T. D. Gian, Tien Dac Lai, Thien Van Luong, Kok-Seng Wong, and V.-D. Nguyen, "HPE-Li: WiFi-enabled Lightweight Dual Selective Kernel Convolution for Human Pose Estimation" in *Proc.  18th European Conference on Computer Vision (ECCV),* Sept. 2024, Milano, Italy, pp.1-18. [ECCV](https://www.ecva.net/papers/eccv_2024/papers_ECCV/papers/04496.pdf){.text-primary .text-decoration-none .fw-bolder}
   - T. D. Gian, D. T. Tran, Q.-V. Pham, L.-N. Tran and V.-D. Nguyen, "Multimodal Human Pose Estimation: A Wi-Fi-Driven Approach With Adaptive Kernel Selection," *IEEE Transactions on Artificial Intelligence*, vol. 7, no. 5, pp. 2941-2955, May 2026.
   - X. Hoang Nguyen, V.-D. Nguyen, Q. -T. Luu, T. Dinh Gian and O.-S. Shin, "Robust WiFi Sensing-Based Human Pose Estimation Using Denoising Autoencoder and CNN With Dynamic Subcarrier Attention," *IEEE Internet of Things Journal*, vol. 12, no. 11, pp. 17066-17079, June, 2025.
   - H. T. Nguyen, V.-D. Nguyen, *et al.*, "Energy Efficiency for Massive MIMO Integrated Sensing and Communication Systems," *IEEE Journal on Selected Areas in Communications,* vol. 44, pp. 165-180, 2026.
   - B. M. Tuan, V.-D. Nguyen, *et al.*, "Deep Learning-Driven Friendly Jamming for Secure Multicarrier ISAC Under Channel Uncertainty," *IEEE Transactions on Communications*, vol. 74, pp. 6332-6348, 2026.
   - P. Zivuku, V.-D. Nguyen, N. T. Nguyen, K. Ntontin, S. Chatzinotas and B. Ottersten, "Resource Allocation for RIS-Enhanced OFDM-MIMO ISAC Systems," *IEEE Transactions on Communications*, vol. 74, pp. 1777-1792, 2026.
   - N. T. Nguyen, V.-D. Nguyen, H. V. Nguyen, H. Q. Ngo, A. L. Swindlehurst and M. Juntti, "Performance Analysis and Power Allocation for Massive MIMO ISAC Systems," *IEEE Transactions on Signal Processing,* vol. 73, pp. 1691-1707, 2025.



### 5G/6G (Open RAN, Slicing, Full-Duplex)
   - Q.-T. Luu *et al.*, "Network Slicing With Flexible VNF Order: A Branch-and-Bound Approach," *IEEE Transactions on Network and Service Management,* vol. 23, pp. 3805-3818, 2026.
   - B.-M. Vu, N. T. Dang, S. Moon, O.-S. Shin and V.-D. Nguyen, "Optimizing Mixed FSO-RF Downlink Systems With Active RIS and SLIPT-Enabled UAV-BSs," *IEEE Transactions on Communications,* vol. 74, pp. 3600-3616, 2026.
   - T.-V. Truong *et al.*, "Accelerating Resource Allocation in Open RAN Slicing via Deep Reinforcement Learning," *IEEE Transactions on Network and Service Management*, vol. 23, pp. 3055-3070, 2026
   - F. Kavehmadavani, T. X. Vu, V.-D. Nguyen and S. Chatzinotas, "Intelligent User Association and Scheduling in Open RAN: A Hierarchical Optimization Framework," *IEEE Transactions on Communications,* vol. 73, no. 11, pp. 11574-11589, Nov. 2025.
   - F. Kavehmadavani, V.-D. Nguyen, T. X. Vu and S. Chatzinotas, "Empowering Traffic Steering in 6G Open RAN With Deep Reinforcement Learning," *IEEE Transactions on Wireless Communications*, vol. 23, no. 10, pp. 12782-12798, Oct. 2024.
   - V.-D. Nguyen *et al*., "Network-Aided Intelligent Traffic Steering in 6G O-RAN: A Multi-Layer Optimization Framework," in *IEEE Journal on Selected Areas in Communications,* vol. 42, no. 2, pp. 389-405, Feb. 2024.
   - N. T. Thanh Van, N. C. Luong, S. Feng, V.-D. Nguyen and D. I. Kim, "Evolutionary Games for Dynamic Network Resource Selection in RSMA-Enabled 6G Networks," *IEEE Journal on Selected Areas in Communications,* vol. 41, no. 5, pp. 1320-1335, May 2023.
   - D. Van Huynh, V.-D. Nguyen, S. Chatzinotas, S. R. Khosravirad, H. V. Poor and T. Q. Duong, "Joint Communication and Computation Offloading for Ultra-Reliable and Low-Latency With Multi-Tier Computing," *IEEE Journal on Selected Areas in Communications,* vol. 41, no. 2, pp. 521-537, Feb. 2023.
   - N. T. Nguyen, V.-D. Nguyen, H. V. Nguyen, H. Q. Ngo, S. Chatzinotas and M. Juntti, "Spectral Efficiency Analysis of Hybrid Relay-Reflecting Intelligent Surface-Assisted Cell-Free Massive MIMO Systems," *IEEE Transactions on Wireless Communications*, vol. 22, no. 5, pp. 3397-3416, May 2023.
   - H. V. Nguyen *et al.*, "On the Spectral and Energy Efficiencies of Full-Duplex Cell-Free Massive MIMO," *IEEE Journal on Selected Areas in Communications*, vol. 38, no. 8, pp. 1698-1718, Aug. 2020.
   - V.-D. Nguyen, H. V. Nguyen, O. A. Dobre and O.-S. Shin, "A New Design Paradigm for Secure Full-Duplex Multiuser Systems," *IEEE Journal on Selected Areas in Communications*, vol. 36, no. 7, pp. 1480-1498, July 2018.
   - V.-D. Nguyen, H. D. Tuan, T. Q. Duong, H. V. Poor and O.-S. Shin, "Precoder Design for Signal Superposition in MIMO-NOMA Multicell Networks," *IEEE Journal on Selected Areas in Communications*, vol. 35, no. 12, pp. 2681-2695, Dec. 2017.


### Internet of Things 
   - S. H. Wanasekara, V.-D. Nguyen, K.-S. Wong, M.-D. Nguyen, S. Chatzinotas and O. A. Dobre, "SC-GIR: Goal-Oriented Semantic Communication via Invariant Representation Learning for Image Transmission," *IEEE Transactions on Mobile Computing*, vol. 25, no. 2, pp. 1483-1498, Feb. 2026.
   - C.-H. Nguyen *et al.*, "Encrypted Data Caching and Learning Framework for Robust Federated Learning-Based Mobile Edge Computing," *IEEE/ACM Transactions on Networking*, vol. 32, no. 3, pp. 2705-2720, June 2024.
   - D. Van Huynh, V.-D. Nguyen, S. R. Khosravirad, G. K. Karagiannidis and T. Q. Duong, "Distributed Communication and Computation Resource Management for Digital Twin-Aided Edge Computing With Short-Packet Communications," *IEEE Journal on Selected Areas in Communications,* vol. 41, no. 10, pp. 3008-3021, Oct. 2023.
   - V.-D. Nguyen, S. Chatzinotas, B. Ottersten and T. Q. Duong, "FedFog: Network-Aware Optimization of Federated Learning Over Wireless Fog-Cloud Systems," *IEEE Transactions on Wireless Communications,* vol. 21, no. 10, pp. 8581-8599, Oct. 2022.
   - D.-H. Tran, V.-D. Nguyen, S. Chatzinotas, T. X. Vu and B. Ottersten, "UAV Relay-Assisted Emergency Communications in IoT Networks: Resource Allocation and Trajectory Optimization," *IEEE Transactions on Wireless Communications*, vol. 21, no. 3, pp. 1621-1637, March 2022.
   - V.-D. Nguyen, S. K. Sharma, T. X. Vu, S. Chatzinotas and B. Ottersten, "Efficient Federated Learning Algorithm for Resource Allocation in Wireless IoT Networks," *IEEE Internet of Things Journal,* vol. 8, no. 5, pp. 3394-3409, 1 March1, 2021.


### Smart Aquaculture
   - P. H. Nguyen, B. H. Ngo, M. P. Tran, C. D. Do and V.-D. Nguyen, "FISHER: Gradient-Decoupled Hierarchical Multi-Task Learning for Fine-Grained Aquatic Species Recognition", *IEEE Transactions on Circuits and Systems for Video Technology* (under review).
   - Doanh Cao Bui, Hung Ba Ngo, Cuong Danh Do, and Van-Dinh Nguyen, "SPACO-VLM: Spatial Awareness of Coral Reefs in Large Vision–Language Models for Visual Question Answering", *Pattern Recognition* (under review).
   - Quynh-Hoa N. Dam, Phuc H. Nguyen, Mai P. Tran, Cong-Son Trinh, Trung T. Nguyen, Ninh N. G. Nguyen, Tuan-Dung Bui, Hung B. Ngo, Cuong D. Do, Dinh V. Dzung and Van Dinh Nguyen, "From Monitoring to Action: A Comprehensive Survey of Autonomous Decision-Making in Smart Aquaculture Systems​", *Computers and Electronics in Agriculture* (under review).
   
   


## Full Publication List

```{r setup}
library(tidyverse)
library(RefManageR)
library(htmltools)

`%||%` <- function(a, b) if (is.null(a) || length(a) == 0) b else a
nz_chr <- function(x) ifelse(is.na(x) | trimws(x) == "", NA_character_, x)

strip_braces <- function(x) {
  if (is.null(x) || length(x) == 0) return(NA_character_)
  y <- as.character(x)
  gsub("[{}]", "", y, perl = TRUE)
}

fmt_authors_card <- function(entry) {
  au <- entry$author
  if (is.null(au) || length(au) == 0) return(NA_character_)
  fmt_one <- function(a) {
    fam_vec <- a$family
    if (length(fam_vec)) paste(as.character(fam_vec), collapse = " ") else ""
  }
  pieces <- vapply(au, fmt_one, character(1))
  pieces <- pieces[nzchar(pieces)]
  if (!length(pieces)) return(NA_character_)
  if (length(pieces) == 1) pieces
  else paste(paste(pieces[-length(pieces)], collapse = ", "), "&", pieces[length(pieces)])
}

get_abstract <- function(entry) {
  abs <- entry$abstract %||% entry$annotation %||% NA_character_
  if (isTRUE(is.na(abs)) || !nzchar(abs)) NA_character_ else abs
}

get_bibtex <- function(entry) {
  out <- tryCatch({
    e <- entry
    if (!is.null(e$note)) e$note <- NULL
    if (!is.null(e$Note)) e$Note <- NULL
    txt <- paste0(utils::toBibtex(e), collapse = "\n")
    txt <- sub(",\\s*\\n?\\s*\\}$", "\n}", txt, perl = TRUE)
    txt <- gsub("\n{3,}", "\n\n", txt)
    txt
  }, error = function(err) NA_character_)
  if (is.na(out) || !nzchar(out)) NA_character_ else out
}

normalize_link <- function(x) {
  y <- as.character(x)
  y[is.na(y)] <- NA_character_
  y <- trimws(y)

  y <- gsub("\\\\_", "_", y)
  
  y[y == "" | tolower(y) == "na"] <- NA_character_

  ok <- !is.na(y)

  doi_pref <- ok & grepl("^doi:\\s*", y, ignore.case = TRUE)
  y[doi_pref] <- sub("^doi:\\s*", "", y[doi_pref], ignore.case = TRUE)
  bare_doi <- ok & grepl("^10\\.", y)
  y[bare_doi] <- paste0("https://doi.org/", y[bare_doi])

  arxiv_pref <- ok & grepl("^arxiv:\\s*", y, ignore.case = TRUE)
  if (any(arxiv_pref)) {
    ids <- sub("^arxiv:\\s*", "", y[arxiv_pref], ignore.case = TRUE)
    ids <- sub("^([^\\s]+).*", "\\1", ids)
    y[arxiv_pref] <- paste0("https://arxiv.org/abs/", ids)
  }

  domain_like <- ok & grepl("^(www\\.|[A-Za-z0-9.-]+\\.[A-Za-z]{2,})(/|$)", y)
  no_scheme   <- ok & !grepl("^https?://", y, ignore.case = TRUE)
  needs_scheme <- domain_like & no_scheme
  y[needs_scheme] <- paste0("https://", y[needs_scheme])

  y
}
```

```{r}
#| label: build-rows

bib  <- ReadBib("publications.bib", check = FALSE)
keys <- names(bib)

extra_links <- tibble(key = character(), preprint = character(), materials = character())

rows <- tibble(
  key   = keys,
  entry = lapply(keys, function(k) bib[k])
) |>
  mutate(
    title        = map_chr(entry, ~ strip_braces(.x$title %||% "")),
    authors_card = map_chr(entry, fmt_authors_card),
    year         = map_chr(entry, ~ {
      y <- .x$year %||% .x$date %||% ""
      if (is.list(y)) y$year %||% "" else as.character(y)
    }),
    venue        = map_chr(entry, ~ strip_braces(.x$journal %||% .x$booktitle %||% .x$publisher %||% "")),
    abstract     = map_chr(entry, get_abstract),
    bibtex       = map_chr(entry, get_bibtex),

    doi          = map_chr(entry, ~ .x$doi %||% NA_character_),
    url_fallback = map_chr(entry, ~ .x$url %||% NA_character_),

    preprint_raw  = map_chr(entry, ~ { v <- .x$preprint;  if (is.null(v) || length(v)==0) NA_character_ else as.character(v[[1]]) }),
    materials_raw = map_chr(entry, ~ { v <- .x$materials; if (is.null(v) || length(v)==0) NA_character_ else as.character(v[[1]]) }),

    has_preprint_key  = map_lgl(entry, ~ !is.null(.x$preprint)  && length(.x$preprint)  > 0),
    has_materials_key = map_lgl(entry, ~ !is.null(.x$materials) && length(.x$materials) > 0)
  ) |>
  left_join(extra_links, by = "key") |>
  mutate(
    preprint_val  = coalesce(preprint,  preprint_raw),
    materials_val = coalesce(materials, materials_raw)
  ) |>
  select(-any_of(c("preprint", "materials"))) |>
  mutate(
    preprint_url  = normalize_link(preprint_val),
    materials_url = normalize_link(materials_val)
  ) |>
  mutate(
    doi_url = normalize_link(
      if_else(
        nzchar(doi %||% ""),
        str_glue("https://doi.org/{doi}"),
        if_else(nzchar(preprint_url %||% ""), preprint_url, url_fallback)
      )
    )
  ) |>
  mutate(
    primary = map_lgl(entry, ~ tolower(as.character(.x$primary %||% "false")) == "true")
  ) |>
  arrange(desc(year), title)
```

```{css}
/* Group header */
.year-group { margin: 28px 0 8px; }
.year-title { margin: 0; font-size: 1.35rem; border-bottom: 1px solid #e5e7eb; padding-bottom: 2px; }

/* Card + layout */
.pub-card {
  border: 1px solid #e5e7eb;
  border-radius: 14px;
  padding: 16px 16px 10px 16px;
  margin: 14px 0;
  background: #fff;
}
.pub-title { font-weight: 600; font-size: 1.05rem; margin-bottom: 4px; }
.pub-title a { text-decoration: none; }
.pub-meta  { color: #555; font-size: 0.95rem; margin-bottom: 8px; }

/* Actions row */
.pub-actions {
  display: flex; flex-wrap: wrap; gap: 8px 14px; align-items: center;
  margin-top: 8px; margin-bottom: 8px;
}
.pub-actions a {
  text-decoration: none; font-size: 0.92rem;
  border-bottom: 1px dotted #999; color: #0b66c3; cursor: pointer;
}
.pub-actions a.external { border-bottom-style: solid; }

/* Toggle area */
.toggle-area {
  display: none; position: relative;
  border: 1px solid #000; border-radius: 10px;
  padding: 12px 44px 12px 12px; background: #fafafa;
  margin-top: 10px; overflow: auto;
}
.toggle-area .panel-label {
  font-size: 0.82rem; color: #333; font-weight: 600;
  text-transform: uppercase; letter-spacing: 0.03em;
  opacity: 0.85; margin-bottom: 6px;
}
.toggle-area pre { white-space: pre-wrap; word-wrap: break-word; margin: 0; }
.toggle-area .content p { margin: 0 0 0.6em 0; }

/* Copy button */
.copy-btn {
  position: absolute; top: 6px; right: 6px;
  border: 1px solid #ddd; background: #fff; font-size: 0.85rem;
  padding: 4px 8px; border-radius: 6px; cursor: pointer;
}
.copy-btn:active { transform: translateY(1px); }
.copy-toast {
  position: absolute; top: 6px; right: 70px; font-size: 0.8rem;
  background: #333; color: #fff; padding: 3px 7px; border-radius: 6px; display: none;
}

/* Lab-led star on Abstract link */
.pub-actions .lab-star {
  display: inline-flex;
  align-items: center;
  justify-content: center;
  font-size: 0.9rem;
  line-height: 1;
  color: #ffb300;
  user-select: none;
}
.pub-actions .lab-star[role="img"] {
  cursor: default;
}
.pub-actions .lab-star .sr-only {
  position: absolute;
  width: 1px; height: 1px;
  padding: 0; margin: -1px; overflow: hidden;
  clip: rect(0, 0, 0, 0); white-space: nowrap; border: 0;
}
```

```{=html}
<script>
(function() {
  function getCard(el) {
    while (el && !el.classList?.contains('pub-card')) el = el.parentNode;
    return el;
  }
  function showPanel(card, label, html, mode) {
    const area = card.querySelector('.toggle-area');
    const labelEl = area.querySelector('.panel-label');
    const contentEl = area.querySelector('.content');

    // Toggle: if clicking same action while open, collapse
    const current = area.getAttribute('data-current');
    if (current === mode && area.style.display === 'block') {
      area.style.display = 'none';
      area.setAttribute('data-current', '');
      return;
    }

    labelEl.textContent = label;
    if (mode === 'bib') {
      contentEl.innerHTML = '';
      const pre = document.createElement('pre');
      pre.textContent = html;
      contentEl.appendChild(pre);
    } else if (mode === 'abstract') {
      contentEl.textContent = html;
    } else {
      contentEl.innerHTML = html; // citation HTML
    }
    area.style.display = 'block';
    area.setAttribute('data-current', mode);
  }

  // Resource link handler (toggle)
  document.addEventListener('click', function(evt) {
    const a = evt.target.closest('a[data-action]');
    if (!a) return;
    const action = a.getAttribute('data-action');
    const card   = getCard(a);
    if (!card) return;
    evt.preventDefault();

    if (action === 'abstract' || action === 'citation' || action === 'bib') {
      const key = card.getAttribute('data-key');  // <-- Pandoc ref id suffix

      // Build label + payload
      let label = action === 'citation' ? 'Citation' : (action === 'bib' ? 'BibTeX' : 'Abstract');
      let html  = '';

      if (action === 'abstract') {
        const payloadEl = card.querySelector('.payload-abstract');
        const text = (payloadEl?.textContent || 'No abstract available.').trim();
        showPanel(card, label, text, 'abstract');
        return;
      }

      if (action === 'citation') {
        // Pull APA-formatted HTML from hidden #refs list: <div id="ref-KEY">
        const ref = document.querySelector('#ref-' + key);
        html = (ref ? ref.innerHTML : 'Citation unavailable.').trim();
        showPanel(card, label, html, 'citation');
        return;
      }

      if (action === 'bib') {
        const payloadEl = card.querySelector('.payload-bibtex');
        const text = (payloadEl?.textContent || 'No BibTeX available.').trim();
        showPanel(card, label, text, 'bib');
        return;
      }
    }
  }, false);

  // Copy button
  document.addEventListener('click', function(evt) {
    const btn = evt.target.closest('.copy-btn');
    if (!btn) return;
    const card = getCard(btn);
    const area = card.querySelector('.toggle-area');
    const contentEl = area.querySelector('.content');

    let textToCopy = '';
    const pre = contentEl.querySelector('pre');
    if (pre) textToCopy = pre.textContent;
    else textToCopy = contentEl.innerText;

    navigator.clipboard.writeText(textToCopy).then(() => {
      const toast = area.querySelector('.copy-toast');
      toast.style.display = 'inline-block';
      setTimeout(() => { toast.style.display = 'none'; }, 1200);
    }).catch(() => {
      const ta = document.createElement('textarea');
      ta.value = textToCopy;
      document.body.appendChild(ta);
      ta.select();
      try { document.execCommand('copy'); } catch (e) {}
      document.body.removeChild(ta);
    });
  }, false);
})();
</script>
```

```{r}
#| label: render-publications

build_card <- function(
  key, entry, title, authors_card, year, venue,
  abstract, bibtex,
  preprint_url = NA_character_, materials_url = NA_character_,
  doi_url = NA_character_, primary = FALSE, ...
) {
  has_preprint_key  <- !is.null(entry$preprint)  && length(entry$preprint)  > 0
  has_materials_key <- !is.null(entry$materials) && length(entry$materials) > 0

  payloads <- tags$div(
    style = "display:none;",
    tags$div(class = "payload-abstract", abstract %||% ""),
    tags$div(class = "payload-bibtex",  bibtex   %||% "")
  )

  ttl_node <- if (isTRUE(nzchar(doi_url %||% ""))) {
    tags$div(class = "pub-title", tags$a(title, href = doi_url, target = "_blank", rel = "noopener"))
  } else {
    tags$div(class = "pub-title", title)
  }

  meta <- tags$div(
    class = "pub-meta",
    if (nzchar(authors_card %||% "")) {
      tagList(HTML(authors_card), tags$br())
    } else {
      NULL
    },
    tagList(if (nzchar(venue %||% "")) tags$em(venue) else NULL)
  )

  actions <- tags$div(
    class = "pub-actions",
    # Standalone star badge (only if primary)
    if (isTRUE(primary)) tags$span(
      class = "lab-star",
      role  = "img",
      title = "This project was led by the AffCom lab",
      `aria-label` = "This project was led by the AffCom lab",
      "★",
      tags$span(class = "sr-only", " This project was led by the AffCom lab")
    ),
    # Action links
    tags$a("Abstract", href = "#", `data-action`="abstract", role="button"),
    tags$a("Citation", href = "#", `data-action`="citation", role="button"),
    tags$a("BibTeX",   href = "#", `data-action`="bib",      role="button"),
    if (isTRUE(has_preprint_key))
      tags$a("Preprint", class = "external", href = (preprint_url %||% "#"), target = "_blank", rel="noopener"),
    if (isTRUE(has_materials_key))
      tags$a("Materials", class = "external", href = (materials_url %||% "#"), target = "_blank", rel="noopener")
  )

  toggle_panel <- tags$div(
    class = "toggle-area",
    `data-current` = "",
    tags$button(class = "copy-btn", "Copy"),
    tags$span(class = "copy-toast", "Copied!"),
    tags$div(class = "panel-label", "—"),
    tags$div(class = "content")
  )

  tags$div(class = "pub-card", `data-key` = key, ttl_node, meta, actions, toggle_panel, payloads)
}

years <- rows |>
  distinct(year) |>
  arrange(desc(year)) |>
  pull(year)

groups <- lapply(years, function(y) {
  subset <- rows |> filter(year == y)

  subset_min <- subset |>
    select(
      key, entry, title, authors_card, year, venue,
      abstract, bibtex,
      preprint_url, materials_url, doi_url, primary
    )
  cards <- pmap(subset_min, build_card)

  tags$div(
    class = "year-group",
    tags$h2(class = "year-title anchored", id = paste0("y-", y), str_to_title(y)),
    tags$div(cards)
  )
})

browsable(tags$div(groups))
```


